---
title: "WTP descriptives"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# load packages
```{r}
library(tidyverse)
```

# define palettes
```{r}
food = wesanderson::wes_palette("Zissou1", 2, "continuous")
```

# load and tidy data
```{r}
data = read.csv("~/Documents/code/sanlab/DEV_scripts/fMRI/fx/multiconds/WTP/betaseries/events.csv", stringsAsFactors = FALSE) %>%
  mutate(bid = ifelse(bid == "NULL", NA, bid),
         bid = as.integer(bid),
         health = as.factor(health),
         liking = as.factor(liking)) %>%
  filter(wave == 1)
```

# check responses
Check if wrong buttons were used (i.e., not 5-8)

* DEV002 = wrong button box (i.e. 1-4) used 
* DEV007 = wrong button box (i.e. 1-4) used
* DEV011 = code normally
* DEV017 = exclude; can't tell if they're missed responses or incorrect placement of fingers
* DEV019 = exclude; can't tell if they're missed responses or incorrect placement of fingers
* DEV032 = code normally
* DEV033 = incorrect placement of fingers; recode runs 1-3
* DEV054 = exclude; technical error?
* DEV061 = code normally

```{r}
subs = data %>%
  mutate(bid = as.character(bid)) %>%
  group_by(subjectID, run, bid) %>%
  summarize(n = n()) %>%
  spread(bid, n) %>%
  mutate(messed = ifelse(!is.na(`2`), "yes", NA),
         messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", messed)) %>%
  filter(messed == "yes") %>% 
  ungroup() %>% 
  select(subjectID) %>% 
  unique()

data %>%
  mutate(bid = as.character(bid)) %>%
  group_by(subjectID, run, bid) %>%
  summarize(n = n()) %>%
  spread(bid, n) %>%
  mutate(messed = ifelse(!is.na(`2`), "yes", NA),
         messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", messed)) %>%
  filter(subjectID %in% subs$subjectID)
```

# recode and exclude
Exclusions

* Didn't scan: DEV002, DEV007
* MRI motion and data quality exclusions: DEV001, DEV020, DEV032, DEV047, DEV063, DEV067, DEV078
* Button box exclusions: DEV017, DEV019, DEV054

Recoding

* DEV033: recode runs1-3, but if liking rating < 3, leave as missing
```{r}
data.ex = data %>%
  filter(!subjectID %in% c("DEV002", "DEV007", "DEV001", "DEV020", "DEV032", "DEV047", "DEV063", "DEV067", "DEV078", "DEV017", "DEV019", "DEV054")) %>%
  mutate(bid = ifelse(subjectID == "DEV033" & !run == "run4", bid - 1, bid),
         bid = ifelse(subjectID == "DEV033" & !run == "run4" & is.na(bid) & liking_rating > 2, 8, bid),
         bid = (bid - 5) / 2)
```

# repeated measures correlation between liking and bid value
```{r}
# correlation
data.ex %>%
  ggplot(aes(liking_rating, bid, color = health)) +
    geom_point(position = "jitter", alpha = .1) + 
    geom_smooth(method = "lm", size = 1.5) +
    scale_color_manual(values = food) +
    theme_minimal()

# correlation by liking condition
data.ex %>%
  ggplot(aes(liking_rating, bid, color = health)) +
    geom_point(position = "jitter", alpha = .1) + 
    geom_smooth(method = "lm", size = 1.5) +
    facet_grid(~liking) +
    scale_color_manual(values = food) +
    theme_minimal()

# average correlation overlaid on individual correlations
data.ex %>%
  ggplot(aes(liking_rating, bid, color = health)) +
    geom_line(aes(group = interaction(subjectID, health)), stat = "smooth", method = "lm", alpha = .15, se = FALSE) +
    geom_line(stat = "smooth", method = "lm", size = 1.5) +
    scale_color_manual(values = food) +
    theme_minimal()

# average correlation overlaid on individual correlations by liking condition
data.ex %>%
  ggplot(aes(liking_rating, bid, color = health)) +
    geom_line(aes(group = interaction(subjectID, health)), stat = "smooth", method = "lm", alpha = .15, se = FALSE) +
    geom_line(stat = "smooth", method = "lm", size = 1.5) +
    facet_grid(~liking) +
    scale_color_manual(values = food) +
    theme_minimal()

# healthy
data.ex %>%
  filter(health == "unhealthy") %>%
  mutate(subjectID = as.factor(subjectID)) %>% 
  select(subjectID, liking_rating, bid) %>%
  rmcorr::rmcorr(subjectID, liking_rating, bid, .)

# unhealthy
data.ex %>%
  filter(health == "unhealthy") %>%
  mutate(subjectID = as.factor(subjectID)) %>% 
  select(subjectID, liking_rating, bid) %>%
  rmcorr::rmcorr(subjectID, liking_rating, bid, .)

# 4 conditions separately
data.ex %>%
  mutate(subjectID = as.factor(subjectID)) %>% 
  group_by(health, liking) %>%
  select(subjectID, liking_rating, bid) %>%
  do(rmcorr::rmcorr(subjectID, liking_rating, bid, .) %>%
      tibble() %>%
      rename("model" = ".") %>%
      mutate(variable = c("r", "n", "p", "CI", "call", "vars")) %>%
      filter(variable %in% c("r", "n", "p")) %>%
      mutate(tidied = purrr::map(model, broom::tidy)) %>%
      select(variable, tidied) %>%
      unnest() %>%
      spread(variable, x)) %>%
      mutate_if(is.numeric, funs(round(., 2)))
```

# plot means as a function of health and liking condition
```{r}
data.ex %>%
  mutate(liking_rating = (liking_rating - 1) / 2) %>%
  gather(type, rating, bid, liking_rating) %>%
  ggplot(aes(type, rating, fill = health, alpha = liking)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = food) +
    scale_y_continuous(limits = c(0,1.5)) +
    theme_minimal()

data.ex %>%
  ggplot(aes(bid, fill = health)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    scale_fill_manual(values = food) +
    theme_minimal()

data.ex %>%
  ggplot(aes(bid, fill = health, alpha = liking)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    facet_grid(~liking) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = food) +
    theme_minimal()
```

# plot distribution of difference scores
* positive diff = higher when bidding, negative diff = lower when bidding
```{r}
data.ex %>%
  mutate(liking_rating = (liking_rating - 1) / 2,
         diff = bid - liking_rating) %>%
  ggplot(aes(diff, fill = health)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    scale_fill_manual(values = food) +
    labs(x = "difference (bid - liking)") +
    theme_minimal()

data.ex %>%
  mutate(liking_rating = (liking_rating - 1) / 2,
         diff = bid - liking_rating) %>%
  ggplot(aes(diff, fill = health, alpha = liking)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    facet_grid(~liking) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = food) +
    labs(x = "difference (bid - liking)") +
    theme_minimal()
```

# self-control approach
* bid lower on unhealthy foods
* bid higher on healthy foods
* positive diff = higher when bidding, negative diff = lower when bidding
```{r}
data.sc2 = data.ex %>%
  mutate(liking_rating = (liking_rating - 1) / 2,
         diff = bid - liking_rating,
         selfcontrol_unhealthy = ifelse(health == "unhealthy" & diff < 0, "yes", "no"),
         selfcontrol_healthy = ifelse(health == "healthy" & diff > 0, "yes", "no"),
         selfcontrol = ifelse(selfcontrol_unhealthy == "yes" | selfcontrol_healthy == "yes", "yes", "no"))

data.sc2 %>%
  filter(!is.na(selfcontrol)) %>%
  ggplot(aes(selfcontrol, diff, fill = health, alpha = liking)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = food) +
    theme_minimal()

data.sc2 %>%
  filter(!is.na(selfcontrol)) %>%
  ggplot(aes(diff, fill = health, alpha = liking)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    facet_grid(~selfcontrol) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = food) +
    labs(x = "difference (bid - liking)") +
    theme_minimal()
```

* bid lower on liked, unhealthy foods
* bid higher on disliked, healthy foods
* positive diff = higher when bidding, negative diff = lower when bidding
```{r}
data.sc = data.ex %>%
  mutate(liking_rating = (liking_rating - 1) / 2,
         diff = bid - liking_rating,
         selfcontrol_unhealthy = ifelse(health == "unhealthy" & liking == "liked" & diff < 0, "yes", "no"),
         selfcontrol_healthy = ifelse(health == "healthy" & liking == "disliked" & diff > 0, "yes", "no"),
         selfcontrol = ifelse(selfcontrol_unhealthy == "yes" | selfcontrol_healthy == "yes", "yes", "no"))

data.sc %>%
  filter(!is.na(selfcontrol)) %>%
  ggplot(aes(selfcontrol, diff, fill = health, alpha = liking)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = food) +
    theme_minimal()

data.sc %>%
  filter(!is.na(selfcontrol)) %>%
  ggplot(aes(diff, fill = health, alpha = liking)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    facet_grid(~selfcontrol) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = food) +
    labs(x = "difference (bid - liking)") +
    theme_minimal()
```
