---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
Sys.setenv(R_CONFIG_ACTIVE = Sys.info()["nodename"])
print(Sys.info()["nodename"])

```

```{r}
dropbbox_dir <- config::get("dev_analysis_data_dir")

```



```{r}
time_points <- readr::read_csv(paste0(dropbbox_dir,"/SST_roi_by_time_point.csv"))
```


Now let's see if we can graph putamen...
```{r}
library(ggplot2)
# ggplot(time_points,
#        aes(x=offset, y=`harvardoxford-subcortical_prob_Left Putamen`))+
#   geom_point()+
#   geom_smooth(method="loess",span=2,na.rm=TRUE) + #https://ggplot2.tidyverse.org/reference/geom_smooth.html
#   scale_y_continuous(limits=c(-2.5,2.5))+
#   facet_wrap(~condition)
  
```



we could also subtract the average per TRIAL. Best we subtract the average across all of the offsets. it's a bit arbitrary to use the average over all the areas; the idea is just to get a consistent amount of average.

```{r}
roi_cols <- c("CueFollowing(CS>FS)striatal_cluster_combined")
time_points$tr_roi_mean <- rowMeans(time_points[,roi_cols])
time_points<- 
  time_points %>% group_by(subid,wave) %>%
  mutate(run_mean_across_rois = mean(tr_roi_mean, na.rm = TRUE))

#now mean-center the ROIs
time_points_c<-time_points
#Removed this because it is irrelevant; these are already mean_centered when they come in. need to do a bit of work to see how that is.
# for (roi_col in roi_cols){
#   time_points_c[,roi_col]<-time_points_c[,roi_col]-time_points_c$run_mean_across_rois
# }
```

```{r}
sd(time_points$`harvardoxford-subcortical_prob_Left Putamen`)
sd(time_points_c$`harvardoxford-subcortical_prob_Left Putamen`)
```

```{r}
library(ggplot2)
ggplot(time_points_c,
       aes(x=offset, y=`harvardoxford-subcortical_prob_Left Putamen`,group=interaction(trial_n,subid,wave)))+
  geom_line(alpha=0.2)+
  #geom_point()+
  #geom_smooth(method="loess",span=2,na.rm=TRUE) + #https://ggplot2.tidyverse.org/reference/geom_smooth.html
  scale_y_continuous(limits=c(-2.5,2.5))+
  facet_wrap(~condition)
  
```

Now let's try just graphing the moving average...

```{r}
library(tidyverse)

#get the range of offsets
min_offset<-round(min(time_points_c$offset))
max_offset <- round(max(time_points_c$offset))

seq_size <- 0.1
offset_size<-1
offset_times <- seq(min_offset,max_offset-max(offset_size,seq_size),seq_size)

dt_list<-list()
for (cond in unique(time_points_c$condition)){
  print(cond)
  for (ot_i in offset_times){
  #<-offset_times[[20]]

  tp_at_offset <- time_points_c %>% filter(offset>=ot_i & offset<(ot_i+offset_size) & condition==cond)
  numeric_cols <- colnames(tp_at_offset)[sapply(tp_at_offset,class)=="numeric"]
  tp_at_offset_m <- data.frame(t(colMeans(tp_at_offset[,numeric_cols],na.rm=TRUE)))
  tp_at_offset_m$offset_start<-ot_i
  tp_at_offset_m$condition<-cond
  dt_list<-append(dt_list,list(tp_at_offset_m))
  if((which(ot_i==offset_times)%%20)==0){
    cat(". ")
  }
  

  }
  print("")

}

df_offset<-data.frame(data.table::rbindlist(dt_list))


```

# get the delay to next trial

```{r}

behavioral_data_w_tone_data <- readr::read_csv(paste0(dropbbox_dir,"/sst_behavioral_data_all_w_class_type_reveal_onset.csv"))

# I want to know: what is the time delay from the tone sound to the PERIOD of the next trial?

```


```{r}
#so I want to match each trial up with the _next_ trial
#grab the set of next trials-we want their onset and their duration
#then match that back onto n+1 of their prior trial
trial_df <- behavioral_data_w_tone_data %>% filter(condition!="Cue") %>% 
  arrange(trial_n) %>%
  group_by(subid,waveid,runid) %>%
  mutate(next_trial_n = lead(trial_n,1)) %>%
  ungroup()


next_trial_df <- behavioral_data_w_tone_data %>% 
  filter(condition!="Cue") %>%
  select(trial_n,condition,onset,trial_duration,subid,waveid,runid)


trials_with_next<-merge(
  trial_df,next_trial_df,
  by.x = c("subid","waveid","runid", "next_trial_n"),
  by.y=c("subid","waveid","runid","trial_n"),
  suffixes = c("","_next"))
```


now, mark for each trial the start and end time point of the next trial, and get measures of how long after each trial the next one appears

```{r}
trials_with_next$trial_end_next <- trials_with_next$onset_next+trials_with_next$trial_duration_next
trials_with_next$class_type_reveal_onset_to_next_trial_start<-trials_with_next$onset_next-trials_with_next$class_type_reveal_onset
trials_with_next$class_type_reveal_onset_to_next_trial_end<-trials_with_next$trial_end_next-trials_with_next$class_type_reveal_onset
```

```{r}
hist(trials_with_next$class_type_reveal_onset_to_next_trial_start,breaks = 100)
median(trials_with_next$class_type_reveal_onset_to_next_trial_start)
```



```{r}
hist(trials_with_next$class_type_reveal_onset_to_next_trial_end,breaks = 100)
median(trials_with_next$class_type_reveal_onset_to_next_trial_end)
```
```{r}
hist(trials_with_next$class_type_reveal_onset_to_next_trial_start)
```

```{r}
next_trial_median <- data.frame(
  "next_trial_start_median" = median(trials_with_next$class_type_reveal_onset_to_next_trial_start),
  "next_trial_end_median" = median(trials_with_next$class_type_reveal_onset_to_next_trial_end)
  )

quantiles <- (1:10)/10
# next_trial_gradient <- data.frame(
#   "quantiles" = quantiles,
#   "next_trial_start" = quantile(trials_with_next$class_type_reveal_onset_to_next_trial_start,(1:10)/10),
#   "next_trial_end" = quantile(trials_with_next$class_type_reveal_onset_to_next_trial_end,(1:10)/10)
#   )

gradient_range = seq(floor(min(trials_with_next$class_type_reveal_onset_to_next_trial_start)),ceiling(max(trials_with_next$class_type_reveal_onset_to_next_trial_end)),0.1)

in_range_by_gradient <- sapply(gradient_range,function(tp){
  time_point_is_after_start <- tp > trials_with_next$class_type_reveal_onset_to_next_trial_start
  time_point_is_before_end <- tp < trials_with_next$class_type_reveal_onset_to_next_trial_end
  number_of_trials <- length(trials_with_next$class_type_reveal_onset_to_next_trial_start) 
  return(sum(time_point_is_after_start & time_point_is_before_end)/number_of_trials)
})

next_trial_gradient <- data.frame("tp"=gradient_range,"pct_in_range"=in_range_by_gradient)
```



# do graphs

```{r}


subj_count <- length(unique(time_points_c$subid))
#df_offset_long<-df_offset# %>% pivot_longer(cols=roi_cols,names_to="ROI_fullname",values_to="value")
# df_offset_long$ROI<-stringr::str_extract_all(df_offset_long$ROI_fullname,pattern = "(?<=harvardoxford\\..{0,3}cortical_prob_)(.*)") %>% sub("\\."," ",.)

# unique_rois<-sort(unique(df_offset_long$ROI))
# unique_rois_ordered <- unique_rois[order(unique_rois %>% str_extract("(?<=.{3,5}\\s)(.*)"))]

# df_offset_long$ROI<-factor(df_offset_long$ROI,levels = unique_rois_ordered, ordered=TRUE)

ggplot_time_points_extras <- list(
  geom_vline(xintercept = 0,linetype="dashed"),
  geom_hline(yintercept = 0,linetype="dotted"),
  labs(
    x="time from tone sound or expected time of tone (s)",
    y="mean BOLD activity (no HRF convolution)",
    #title="Stop Signal Task Activity",
    subtitle=paste0("Across ", as.character(subj_count)," subjects with 128 trials each"),
    caption="0 point is the moment of tone sound (Stop trials)\n or expected tone sound based on prior trial (Go trials)\n HRF convolution not applied\n1 s moving averages")
  )

df_offset
  
plot_final<-ggplot(df_offset,
       aes(x=offset_start, y=CueFollowing.CS.FS.striatal_cluster_combined,color=condition))+
  geom_line()+
  #facet_wrap(~ROI,ncol = 2)+
  ggplot_time_points_extras
  
  #geom_point()+
  #geom_smooth(method="loess",span=2,na.rm=TRUE) + #https://ggplot2.tidyverse.org/reference/geom_smooth.html
  #scale_y_continuous(limits=c(-2.5,2.5))
  

```



```{r}


ggsave(plot_final,filename="compare_conditions.pdf",device="pdf",width = 2, height=1,scale=4)

```

It's almost as if there's an "update" signal at t=2, then a "RPE" signal at t=5-10.

## Just stop trials, divided separately


```{r}
# roi_cols <- colnames(df_offset)[grepl("harvardoxford",colnames(df_offset))]

next_trial_gradient$hrf_tp<-next_trial_gradient$tp+5

ggplot(df_offset %>% filter(condition %in% c("FailedStop","CorrectStop")),
       aes(x=offset_start, y=CueFollowing.CS.FS.striatal_cluster_combined,color=condition))+
  #geom_tile(data = next_trial_gradient, aes(x=hrf_tp,alpha=pct_in_range,y=0),fill="#77ff77",color="transparent")+
  #annotate("text",x=10,y=0.22,label="Subsequent Go Trial\nExpected HRF",size=2)+
  geom_line(size=1,alpha=0.7)+
  
  scale_color_viridis_d(option = "C")+
  coord_cartesian(ylim=c(-0.15,0.2))+
  guides(alpha="none",color=guide_legend(title="ROI"))+
  #guides(alpha="none",color=guide_legend(title="ROI",nrow = 2))+
  ggplot_time_points_extras#+
  #theme(legend.position = "bottom")
  

#ggplot(df_offset_long,aes(x=offset_start, y=value,color=ROI,group=intersect(ROI,condition)))+geom_line()
  #geom_point()+
  #geom_smooth(method="loess",span=2,na.rm=TRUE) + #https://ggplot2.tidyverse.org/reference/geom_smooth.html
  #scale_y_continuous(limits=c(-2.5,2.5))
  

```

## CS-FS

Let's now try to contrast these time series to see what the CS-FS looks like. This will be interesting because it's similar to the simple GLM result I got earlier that set me down the path of trying to analyze this.

```{r}
trial_tps_compare_conditions<-df_offset_long %>% pivot_wider(id_cols=c(offset_start),names_from = "condition",values_from="CueFollowing.CS.FS.striatal_cluster_combined")
trial_tps_compare_conditions$CS_minus_FS<-trial_tps_compare_conditions$CorrectStop-trial_tps_compare_conditions$FailedStop
```



```{r}

ggplot(trial_tps_compare_conditions,
       aes(x=offset_start, y=CS_minus_FS))+
  #geom_tile(data = next_trial_gradient, aes(x=tp,alpha=pct_in_range,y=0),fill="#000000",color="transparent")+
  geom_tile(data = next_trial_gradient, aes(x=hrf_tp,alpha=pct_in_range,y=0),fill="#77ff77",color="transparent")+
  #annotate("text",x=4,y=0.25,label="Subsequent Go Trial\nTime Range",size=2)+
  annotate("text",x=10,y=0.22,label="Subsequent Go Trial\nExpected HRF",size=2)+
  scale_alpha_continuous(name="Subsequent go trial range", range=c(0,0.7),labels=scales::percent_format())+
  geom_line(size=1,alpha=0.5)+
  scale_color_viridis_d(option = "C")+
  ggplot_time_points_extras+
  coord_cartesian(ylim=c(-0.1,0.25))+
  labs(y="CS-FS BOLD activity difference")
  
```

OK, so from this graph it is very clear why, during the subsequent trial, we're seeing positive striatum activity, and it is also clear there is a large dip in the same area right after the tone.




<!-- ## find a way to compare activity from the start and end. Is there a sort of habituation effect? -->

<!-- Easy way first. Take just CS or FS, then do one graph per ROI, use color with the order of the task. -->


<!-- ```{r} -->

<!-- roi_cols <- colnames(time_points_c)[grepl("harvardoxford",colnames(time_points_c))] -->

<!-- next_trial_gradient$hrf_tp<-next_trial_gradient$tp+5 -->

<!-- time_points_long<-time_points_c %>% pivot_longer(cols=roi_cols,names_to="ROI",values_to="value") -->

<!-- unique_rois<-sort(unique(time_points_long$ROI)) -->
<!-- unique_rois_ordered <- unique_rois[order(unique_rois %>% str_extract("(?<=.{3,5}\\.)([A-Za-z]*)$"))] -->

<!-- time_points_long$ROI<-factor(time_points_long$ROI,levels = unique_rois_ordered, ordered=TRUE) -->


<!-- for (c_i in unique(time_points_long$condition)){ -->
<!--   c_plot <- ggplot(time_points_long %>% filter(condition==c_i), -->
<!--        aes(x=offset, y=value,color=trial_n))+ -->
<!--   facet_wrap(~ROI)+ -->
<!--   geom_tile(data = next_trial_gradient, aes(x=hrf_tp,alpha=pct_in_range,y=0),fill="#77ff77",color="transparent")+ -->
<!--   annotate("text",x=10,y=0.22,label="Subsequent Go Trial\nExpected HRF",size=2)+ -->
<!--   geom_line(size=1,alpha=0.1)+ -->
<!--   #scale_color_viridis_d(option = "C")+ -->
<!--   #coord_cartesian(ylim=c(-0.1,0.25))+ -->
<!--   ggplot_time_points_extras -->
<!--   print(c_plot) -->

<!-- } -->

<!-- ``` -->

<!-- That doesn't work. OK, let's try putting the activity into buckets of trials (early, mid, late) then graph for those three groups -->


<!-- ```{r} -->
<!-- library(tidyverse) -->

<!-- #get the range of offsets -->
<!-- min_offset<-round(min(time_points_c$offset)) -->
<!-- max_offset <- round(max(time_points_c$offset)) -->

<!-- seq_size <- 0.1 -->
<!-- offset_size<-1 -->
<!-- offset_times <- seq(min_offset,max_offset-max(offset_size,seq_size),seq_size) -->

<!-- dt_list<-list() -->
<!-- time_points_c$trial_bucket<-"" -->
<!-- time_points_c$trial_bucket[time_points_c$trial_n<=40]<-"early" -->
<!-- time_points_c$trial_bucket[time_points_c$trial_n%in% seq(139-40,139,2)]<-"mid" -->
<!-- time_points_c$trial_bucket[time_points_c$trial_n %in% seq(239-40,239,2)]<-"late" -->




<!-- for (cond in unique(time_points_c$condition)){ -->
<!--   print(cond) -->
<!--   for (tb_i in unique(time_points_c$trial_bucket)){ -->

<!--     for (ot_i in offset_times){ -->


<!--       tp_at_offset <- time_points_c %>% filter(offset>=ot_i & offset<(ot_i+offset_size) & condition==cond & trial_bucket==tb_i) -->
<!--       numeric_cols <- colnames(tp_at_offset)[sapply(tp_at_offset,class)=="numeric"] -->
<!--       tp_at_offset_m <- data.frame(t(colMeans(tp_at_offset[,numeric_cols],na.rm=TRUE))) -->
<!--       tp_at_offset_m$offset_start<-ot_i -->
<!--       tp_at_offset_m$condition<-cond -->
<!--       tp_at_offset_m$trial_bucket<-tb_i -->
<!--       dt_list<-append(dt_list,list(tp_at_offset_m)) -->
<!--       if((which(ot_i==offset_times)%%20)==0){ -->
<!--         cat(". ") -->
<!--       } -->
<!--     } -->

<!--   } -->

<!-- } -->

<!-- df_offset_run_buckets<-data.frame(data.table::rbindlist(dt_list)) -->


<!-- ``` -->



<!-- ```{r} -->
<!-- roi_cols <- colnames(df_offset_run_buckets)[grepl("harvardoxford",colnames(df_offset_run_buckets))] -->
<!-- df_offset_long<-df_offset_run_buckets %>% pivot_longer(cols=roi_cols,names_to="ROI",values_to="value") -->


<!-- df_offset_long <- df_offset_long[!is.nan(df_offset_long$tr), ] -->
<!-- df_offset_long$trial_bucket<-factor(df_offset_long$trial_bucket, levels=c("early","mid","late")) -->
<!-- df_offset_long$ROI_label<-df_offset_long$ROI %>% as.character %>% stringr::str_extract_all(pattern = "(?<=harvardoxford\\..{0,3}cortical_prob_)(.*)") %>% unlist -->
<!-- unique_rois<-sort(unique(df_offset_long$ROI_label)) -->
<!-- unique_rois_ordered <- unique_rois[order(unique_rois %>% str_extract("(?<=.{3,5}\\.)([A-Za-z]*)$"))] -->

<!-- df_offset_long$ROI_label<-factor(df_offset_long$ROI_label,levels = unique_rois_ordered, ordered=TRUE) -->


<!-- for (c_i in unique(df_offset_long$condition)){ -->
<!--   c_plot <- ggplot(df_offset_long  %>% filter(condition==c_i),#filter(condition==c_i), -->
<!--          aes(x=offset_start, y=value,color=trial_bucket,group=trial_bucket))+ -->
<!--     facet_wrap(~ROI_label,ncol = 4)+ -->
<!--     #geom_tile(data = next_trial_gradient, aes(x=hrf_tp,alpha=pct_in_range,y=0),fill="#77ff77",color="transparent")+ -->
<!--     annotate("text",x=10,y=0.22,label="Subsequent Go Trial\nExpected HRF",size=2)+ -->
<!--     geom_line(size=1,alpha=0.5)+ -->
<!--     #scale_color_viridis_d(option = "C")+ -->
<!--     #coord_cartesian(ylim=c(-0.1,0.25))+ -->
<!--     ggplot_time_points_extras+ -->
<!--       labs( -->
<!--       title="Stop Signal Task Activity", -->
<!--       subtitle=paste0(c_i) -->
<!--     ) -->


<!--   #geom_point()+ -->
<!--   #geom_smooth(method="loess",span=2,na.rm=TRUE) + #https://ggplot2.tidyverse.org/reference/geom_smooth.html -->
<!--   #scale_y_continuous(limits=c(-2.5,2.5)) -->
<!--   print(c_plot) -->
<!-- } -->

<!-- ``` -->



<!-- ```{r} -->
<!-- next_trial_gradient$hrf_tp<-next_trial_gradient$tp+5 -->

<!-- for (c_i in unique(df_offset_long$condition)){ -->
<!--   c_plot <- ggplot(df_offset_long %>% filter(condition==c_i & trial_bucket!=""), -->
<!--        aes(x=offset_start, y=value,color=ROI_label))+ -->
<!--   facet_wrap(~trial_bucket,nrow = 1)+ -->
<!--   geom_tile(data = next_trial_gradient, aes(x=hrf_tp,alpha=pct_in_range,y=0),fill="#77ff77",color="transparent",show.legend=FALSE)+ -->
<!--   annotate("text",x=10,y=0.22,label="Subsequent Go Trial\nExpected HRF",size=2)+ -->
<!--   geom_line(size=1,alpha=0.5)+ -->
<!--   scale_color_viridis_d(option = "C")+ -->
<!--   coord_cartesian(ylim=c(-0.5,0.5))+ -->
<!--   ggplot_time_points_extras+ -->
<!--       labs( -->
<!--       title="Stop Signal Task Activity", -->
<!--       subtitle=paste0(c_i) -->
<!--     )+theme(legend.position = "bottom") -->

<!--   print(c_plot) -->
<!-- } -->

<!-- ``` -->

<!-- Can we contrast CS and FS in the way we did above? -->



<!-- ```{r} -->

<!-- trial_tps_compare_conditions<-df_offset_long %>% pivot_wider(id_cols=c(ROI_label,offset_start,trial_bucket),names_from = "condition",values_from="value") -->
<!-- trial_tps_compare_conditions$CS_minus_FS<-trial_tps_compare_conditions$CorrectStop-trial_tps_compare_conditions$FailedStop -->
<!-- ``` -->



<!-- ```{r} -->

<!--   c_plot <- ggplot(trial_tps_compare_conditions %>% filter(trial_bucket!=""), -->
<!--        aes(x=offset_start, y=CS_minus_FS,color=ROI_label))+ -->
<!--   facet_wrap(~trial_bucket,nrow = 1)+ -->
<!--   geom_tile(data = next_trial_gradient, aes(x=hrf_tp,alpha=pct_in_range,y=0),fill="#77ff77",color="transparent",show.legend=FALSE)+ -->
<!--   annotate("text",x=10,y=0.22,label="Subsequent Go Trial\nExpected HRF",size=2)+ -->
<!--   geom_line(size=1,alpha=0.5)+ -->
<!--   scale_color_viridis_d(option = "C")+ -->
<!--   coord_cartesian(ylim=c(-0.5,0.5))+ -->
<!--   ggplot_time_points_extras+ -->
<!--       labs( -->
<!--       title="Stop Signal Task Activity", -->
<!--       subtitle=paste0(c_i), -->
<!--       y="CS-FS BOLD activity difference")+ -->
<!--     theme(legend.position = "bottom") -->
<!-- print(c_plot) -->

<!-- #  -->
<!-- # ggplot(trial_tps_compare_conditions, -->
<!-- #        aes(x=offset_start, y=CS_minus_FS,color=ROI))+ -->
<!-- #   #geom_tile(data = next_trial_gradient, aes(x=tp,alpha=pct_in_range,y=0),fill="#000000",color="transparent")+ -->
<!-- #   geom_tile(data = next_trial_gradient, aes(x=hrf_tp,alpha=pct_in_range,y=0),fill="#77ff77",color="transparent")+ -->
<!-- #   #annotate("text",x=4,y=0.25,label="Subsequent Go Trial\nTime Range",size=2)+ -->
<!-- #   annotate("text",x=10,y=0.22,label="Subsequent Go Trial\nExpected HRF",size=2)+ -->
<!-- #   scale_alpha_continuous(name="Subsequent go trial range", range=c(0,0.7),labels=scales::percent_format())+ -->
<!-- #   geom_line(size=1,alpha=0.5)+ -->
<!-- #   scale_color_viridis_d(option = "C")+ -->
<!-- #   ggplot_time_points_extras+ -->
<!-- #   coord_cartesian(ylim=c(-0.1,0.25))+ -->
<!-- #   labs(y="CS-FS BOLD activity difference") -->

<!-- ``` -->



<!-- There are a different distribution of the number of trials for each condition, but not in a way that clearly could produce the discrepancy I'm observing above. -->
<!-- ```{r} -->
<!-- time_points_c %>% filter(trial_bucket!="") %>% group_by(condition,trial_bucket) %>% summarize(trial_count=n()) -->
<!-- ``` -->



# Re-scale the models


```{r}
load("modeling_t_5_10-activity.RData")
```


Looks like below, the `model_full_effects_incc_abs` y variable is corret, buecase the effect for `conditionFailedStop` matches the difference between CS and FS on teh graph.

However, we might want to re-do the model using z-values for P_stop_trial_change and post_pre_rt_change in order to get more realistic values.




```{r}
summary(model_full_effects_incc_abs)
summary(model_full_effects_incc)
```


```{r}


subj_count <- length(unique(time_points_c$subid))
ggplot(df_offset,
       aes(x=offset_start, y=CueFollowing.CS.FS.striatal_cluster_combined,color=condition))+
  geom_line()+
  #facet_wrap(~ROI,ncol = 2)+
  ggplot_time_points_extras
  
  model_full_effects_incc_abs

```



```{r}

model_full_effects_incc <- lme4::lmer(
   med_post_trial_z ~ trial_n_s+ condition + P_stop_trial_change+ post_pre_rt_change + (1 +post_pre_rt_change  + P_stop_trial_change  | subid),
  trial_neural_behav_roi %>% filter(trial_n>50 & condition %in% c("CorrectStop","FailedStop"))
  )
summary(model_full_effects_incc)


```


```{r}

model_full_effects_abs <- lme4::lmer(
   med_post_trial ~ trial_n_s+ condition + P_stop_trial_change+ post_pre_rt_change + (1 +post_pre_rt_change  + P_stop_trial_change  | subid),
  trial_neural_behav_roi %>% filter(trial_n>50 & condition %in% c("CorrectStop","FailedStop"))
  )
summary(model_full_effects_abs)
```


```{r}

model_full_effects_x_zs <- lme4::lmer(
   med_post_trial ~ trial_n_z+ condition + P_stop_trial_change_z+ post_pre_rt_change_z + (1 +post_pre_rt_change_z  + P_stop_trial_change_z  | subid),
  trial_neural_behav_roi %>% filter(trial_n>50 & condition %in% c("CorrectStop","FailedStop"))
  )
summary(model_full_effects_x_zs)
```


Good start, but something's off with the effect of `P_stop_trial_change_z` relative to `post_pre_rt_change_z`. They are both significant, yet `P_stop_trial_change_z` has a very large effect, and dwarfs the `conditionFailedStop` effect, which seems wrong.

```{r}
trial_neural_behav_roi_stop<-trial_neural_behav_roi %>% filter(trial_n>50 & condition %in% c("CorrectStop","FailedStop"))
                                                               
plot(trial_neural_behav_roi_stop$P_stop_trial_change_z,trial_neural_behav_roi_stop$med_post_trial)

plot(trial_neural_behav_roi_stop$post_pre_rt_change_z,trial_neural_behav_roi_stop$med_post_trial)
```
Indeed--`P_stop_trial_change_z` is not really on a normal distribution at least within this sample.

```{r}
ggplot(trial_neural_behav_roi_stop,aes(post_pre_rt_change_z, med_post_trial_z))
plot(trial_neural_behav_roi_stop$post_pre_rt_change_z,trial_neural_behav_roi_stop$med_post_trial_z)
```
That's because it's set relative to _all_ trials and Stop trials are just a relatively narrow range within that. Shouldn't be too much work to create one that's normed on just the stop trials right?

```{r}
trial_neural_behav_roi_stop<- trial_neural_behav_roi_stop %>% 
  mutate(P_stop_trial_change_z_stop = (P_stop_trial_change-mean(P_stop_trial_change))/sd(P_stop_trial_change),
         post_pre_rt_change_z_stop = (post_pre_rt_change_z-mean(post_pre_rt_change_z))/sd(post_pre_rt_change_z)
         )

plot(trial_neural_behav_roi_stop$P_stop_trial_change_z_stop,trial_neural_behav_roi_stop$med_post_trial)
plot(trial_neural_behav_roi_stop$post_pre_rt_change_z_stop,trial_neural_behav_roi_stop$med_post_trial)
```


Alright--now what do we get?

```{r}

model_full_effects_x_zs <- lme4::lmer(
   med_post_trial ~ trial_n_z+ condition + P_stop_trial_change_z_stop+ post_pre_rt_change_z_stop + (1 +P_stop_trial_change_z_stop  + post_pre_rt_change_z_stop  | subid),
  trial_neural_behav_roi_stop)
summary(model_full_effects_x_zs)
```


# Draw estimates on graph


```{r}

#the estimates apply to the median value at the x-range 4 to 10, so use that.
#also label them by condition
#let's add them to the table as additional lines
df_betas_wide <- data.frame(
  "offset_start_begin"=4,
  "offset_start_end"=10,
  "beta_name"="test_beta",
  "condition"="CorrectStop",
  "CueFollowing.CS.FS.striatal_cluster_combined"=0.1,
  ind=(nrow(df_offset)+1):(nrow(df_offset)+1)
)

df_betas <- df_betas_wide %>% tidyr::pivot_longer(cols=c("offset_start_begin","offset_start_end"),
                                                  names_to="point_type",values_to="offset_start")


df_draw <- merge(
  df_offset %>% mutate("dtype"="bold"),
  df_betas %>% mutate("dtype"="beta estimate"),
  by=c(intersect(colnames(df_offset),colnames(df_betas)),"dtype"),all=TRUE
)
  

ggplot(df_draw,
       aes(x=offset_start, y=CueFollowing.CS.FS.striatal_cluster_combined,
           color=condition,
           linetype=dtype,
           group=interaction(condition,dtype)))+
  geom_line()+
  #facet_wrap(~ROI,ncol = 2)+
  ggplot_time_points_extras
```

OK, looks good, but what are the appropriate points to illustrate what I want to say? 

Maybe arrows pointing to +-1 SD??








