---
title: "DEV dicom check"
author: "Dani Cosme, Ben Smith"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: united
    toc: true
    toc_float: 
      collapsed: TRUE
      smooth_scroll: TRUE
    df_print: paged
---
depending on environment, may need to run something like: `setwd("org/dicom_check/")`
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

```

# load packages
```{r}
library(tidyverse)
library(lubridate)
```

# load data
* First download the "sessions" data report from redcap and drop in the `dicom_check` folder
* Then create a new `dicoms.csv` file by printing the file list from talapas using the script:


```
cd /projects/lcni/dcm/sanlab/Berkman/DEV/; 
for i in $(ls -d *); 
  do echo $i >> /projects/sanlab/shared/DEV/DEV_scripts/org/dicom_check/dicoms.csv; 
done
```

* Then you'll want to clean it up--creating it as a new dicoms_cleaned file and then entering info below.

```{r}
#update each of these
dicom_filename <-"dicoms_cleaned_20210908.csv"
redcap_filename <- "DEV-Sessions_DATA_2021-09-08_1937.csv"
```



```{r}
# dicom info
dicoms = read.csv(dicom_filename, header = FALSE) %>%
  rename("folder" = V1)

# redcap session info
redcap_sessions = read.csv(redcap_filename, na.strings = c("")) %>%
  rename("subjectID" = dev_id) %>%
  select(-redcap_event_name) %>%
  group_by(subjectID) %>%
  fill(everything(), .direction = "down") %>%
  fill(everything(), .direction = "up") %>%
  unique() %>%
  gather(session, date, -subjectID) %>%
  mutate(date = ymd(date),
         session = sprintf("redcap_%s", session)) %>%
  spread(session, date) %>%
  select(redcap_date_1, redcap_date_2)
```

# tidy data
```{r}
dicoms_tidy = dicoms %>%
  extract(folder, c("subjectID", "datetime"), "([A-Za-z]{3}[0-9]{3,4})_(.*)", remove = FALSE) %>%
  extract(datetime, "date", "(.*)_.*", remove = FALSE) %>%
  mutate(subjectID = gsub("dev", "DEV", subjectID),
         datetime = ymd_hms(datetime),
         date = ymd(date)) %>%
  filter(!is.na(subjectID) | grepl("DEV", folder)) %>%
  group_by(subjectID) %>%
  mutate(sessionNum = row_number())
```

# summarize
```{r}
# redcap session info
redcap_sessions %>%
  gather(session, date, -subjectID) %>%
  filter(!is.na(date)) %>%
  group_by(session) %>%
  summarize(n = n())

# dicom info
dicoms_tidy %>%
  group_by(sessionNum) %>%
  summarize(n = n())
```

# check incorrectly named dicoms
* DEV_20171214 = test subject, not in the study
* DEV0903_20190607_090700 = DEV093
* TEST999_20180219_170145 = test sub
```{r}
dicoms_tidy %>%
  filter(!grepl("DEV[0-9]{3}$", subjectID))
```


# verify sessions
Check if there are too many sessions or if the session dates are incorrect

Columns `dicom_date_*` are derived from the dicom folder timestamps.

Columns `redcap_date_*` are derived from the redcap sessions.

These should match perfectly.

```{r}
(merged = dicoms_tidy %>%
   arrange(datetime) %>%
   group_by(subjectID) %>%
   mutate(dicom_date = sprintf("dicom_date_%d", row_number())) %>%
   arrange(subjectID) %>%
   select(-datetime) %>%
   spread(dicom_date, date) %>%
   group_by(subjectID) %>%
   fill(everything(), .direction = "up") %>%
   fill(everything(), .direction = "down") %>%
   full_join(., redcap_sessions) %>%
   ungroup() %>%
   filter(!(is.na(dicom_date_1)) & !subjectID == "EST999"))

merged_check = merged %>%
  select(-c(folder, sessionNum)) %>%
  unique() %>%
  mutate(correct_dicom_date_1 = ifelse(dicom_date_1 == redcap_date_1, 1, 0),
         correct_dicom_date_2 = ifelse(dicom_date_2 == redcap_date_2, 1, 0),
         check_missing1 = ifelse((is.na(redcap_date_1) & !is.na(dicom_date_1)) | (!is.na(redcap_date_1) & is.na(dicom_date_1)), 1, 0),
         check_missing2 = ifelse((is.na(redcap_date_2) & !is.na(dicom_date_2)) | (!is.na(redcap_date_2) & is.na(dicom_date_2)), 1, 0),
         check_order = ifelse(dicom_date_1 == redcap_date_2 | dicom_date_2 == redcap_date_1, 1, 0), #| session3 == redcap_date_2 | session4 == redcap_date_2
         duration = ifelse(!is.na(dicom_date_2), dicom_date_2 - dicom_date_1, NA))
merged_check %>%
  filter(!correct_dicom_date_1 == 1 | !correct_dicom_date_2 == 1 | duration < 24) %>% #!is.na(session3) | !is.na(session4) |
  select(subjectID, correct_dicom_date_1, correct_dicom_date_2, check_missing1, check_missing2, check_order, duration, redcap_date_1, dicom_date_1, redcap_date_2, dicom_date_2) #session3, session4

```

Duplicates
```{r}
(duplicates = dicoms_tidy %>%
  arrange(datetime) %>%
  left_join(., merged) %>%
  mutate(correct_dicom_date_1 = ifelse(dicom_date_1 == redcap_date_1, 1, 0),
         correct_dicom_date_2 = ifelse(dicom_date_2 == redcap_date_2, 1, 0),
         check_order = ifelse(dicom_date_1 == redcap_date_2 | dicom_date_2 == redcap_date_1 , 1, 0), #| session3 == redcap_date_2 | session4 == redcap_date_2
         duration = ifelse(!is.na(dicom_date_2), dicom_date_2 - dicom_date_1, NA)) %>%
  select(folder, subjectID, datetime, correct_dicom_date_1, correct_dicom_date_2, check_order, duration, redcap_date_1, dicom_date_1, redcap_date_2, dicom_date_2) %>% #, session3, session4
  filter(datetime %in% dicoms_tidy[duplicated(dicoms_tidy$datetime),]$datetime))
```

Wrong dicom_date_1 date
* DEV032 = wrong date in redcap
```{r}
merged_check %>%
  filter(!subjectID %in% duplicates$subjectID) %>%
  filter(!correct_dicom_date_1 == 1)
```

Wrong dicom_date_2 date
* DEV038 = wrong date in redcap
* DEV126 = wrong date in redcap
```{r}
merged_check %>%
  filter(!subjectID %in% duplicates$subjectID) %>%
  filter(!correct_dicom_date_2 == 1)
```

Missing dicom_date_1 date

* DEV007 = pilot sub that was deleted from redcap
* DEV0903 = DEV093
```{r}
merged_check %>%
  filter(!subjectID %in% duplicates$subjectID) %>%
  filter(check_missing1 == 1)
```

Missing dicom_date_2 date

* DEV0903 = DEV093

```{r}
merged_check %>%
  filter(!subjectID %in% duplicates$subjectID) %>%
  filter(check_missing2 == 1)
```

Subs run on dates with messed up files

```{r}
dates_1 = merged_check %>%
  filter(!correct_dicom_date_1 == 1 | check_missing1 == 1 | check_order == 1 | duration < 24) %>%
  filter(!subjectID %in% duplicates$subjectID) %>%
  ungroup() %>%
  gather(session, date, starts_with("dicom_date"), starts_with("redcap_date")) %>%
  select(date) %>%
  unique() %>%
  filter(!is.na(date))

dates_2 = merged_check %>%
  filter(!correct_dicom_date_2 == 1 | check_missing2 == 1 | duration < 24) %>%
  filter(!subjectID %in% duplicates$subjectID) %>%
  ungroup() %>%
  gather(session, date, starts_with("dicom_date"), starts_with("redcap_date")) %>%
  select(date) %>%
  unique() %>%
  filter(!is.na(date))
```

session 1 errors

```{r}
dicoms_tidy %>%
  filter(date %in% dates_1$date) %>%
  arrange(datetime) %>%
  left_join(., merged) %>%
  mutate(check = ifelse(dicom_date_1 != redcap_date_1, 1, 0),
         duration = ifelse(!is.na(dicom_date_2), dicom_date_2 - dicom_date_1, NA)) %>%
  select(folder, subjectID, sessionNum, datetime, check, duration, redcap_date_1, dicom_date_1, redcap_date_2, dicom_date_2)


```


session 2 errors

```{r}


dicoms_tidy %>%
  filter(date %in% dates_2$date) %>%
  arrange(datetime) %>%
  left_join(., merged) %>%
  mutate(check = ifelse(dicom_date_2 != redcap_date_2, 1, 0),
         duration = ifelse(!is.na(dicom_date_2), dicom_date_2 - dicom_date_1, NA)) %>%
  select(folder, subjectID, sessionNum, datetime, check, duration, redcap_date_1, dicom_date_1, redcap_date_2, dicom_date_2)
```
# Further investigation

two DICOM folders missing subject IDs:
 - DEV_20210608_170401
 - DEV_20210714_173417
 
```{r}
dates_from_dicoms_with_sid_missing <- as.Date(c("2021-06-08","2021-07-14"))

redcap_sessions %>% filter(redcap_date_1 %in% dates_from_dicoms_with_sid_missing | redcap_date_2 %in% dates_from_dicoms_with_sid_missing)
```
 

# Issue breakdown (log of issues fixed)

Don't forget to ensure that new_subject_list.txt, when it has been generated, excludes all the folders as below that it should be excluding.
**Remove**  
DEV018_20181025_190858  
DEV012_20190111_090124  
DEV068_20181128_101017  
DEV073_20190312_085608  
DEV084_20190314_165822
159_20200126_115140 (this is the same as DEV159_20200126_115140; Paul & Ben both inspected on 2021-03-24)
  
**Merge**  
DEV012_20180806_173955 and DEV012_20180806_181546 into DEV012_20180806_173955  
  
**Dates wrong on redcap**  
DEV032 2018-07-11 instead of 2018-07-25 (rescheduled?)  
DEV038 2018-10-16 instead of 2018-10-19 (rescheduled?)  
DEV126 2019-08-20 instead of 2019-08-16 (rescheduled?)  
  
**Missing**  
DEV029 missing session 1 (2018-08-08) --> found in wrong folder 
DEV063 missing session 1 (2018-12-07) --> found in wrong folder
DEV126 missing session 1 (2019-07-17) --> dates confirmed on calpendo; wrong folder??  
  
**Rename/remap**  

Input DICOM folders are not renamed. The subject IDs are manually remapped in make_conversion_list.Rmd. Not sure what happens after that...maybe nothing.

DEv025_20180827_163615 --> DEV025_20180827_163615  
DEV0903_20190607_090700 --> DEV093_20190607_090700
DEV_20210714_173417 --> DEV205_20210714_173417
DEV_20210608_170401 --> DEV198_20210608_170401

# Outstanding potentially unresolved issues

 - DEV167 has a session duration that is only 21 days between wave 1 and 2.
 - Dani's script notes that DEV 166 was on the same day
 - We're ignoring redcap dates 3 and subsequent. Not sure if this is OK or not.

**Files manually excluded from before August 2019**

phantom_20181211_112538
Phantom^of
the
opera_20180430_110701
TEST999_20180219_170145
test
dev_20180219_155612
Wwe_20180131_135555

**files manually excluded since August 2019**

 - 159_20200126_115140
 - Matlabtest_20191023_154406
 - matlabtest2_20191025_121247