---
title: "DEV Survey Check"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: united
    toc: true
    toc_float: 
      collapsed: TRUE
      smooth_scroll: TRUE
    df_print: paged
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE, error=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Packages
```{r packages, warning = FALSE, message = FALSE, error = FALSE}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}

if (!require(knitr)) {
  install.packages('knitr')
}

if (!require(devtools)) {
  install.packages('devtools')
}

if (!require(scorequaltrics)) {
  devtools::install_github('jflournoy/qualtrics')
}
```

## Define variables
```{r variables}
cred_file_location = '~/credentials.yaml.DEFAULT'
sid_column_name = 'Login'
survey_name_filter = 'DEV'
sid_pattern = 'DEV[0-9]{3}'
exclude_sid = '^99|DEV737' # subject IDs to exclude
```

## Pull survey list from Qualtrics
To do this, you'll need a Qualtrics API token saved in credentials file on your local machine. If you don't have a file, follow these steps to create one:

1. Generate an API token for Qualtrics. Follow the steps outlined [here](https://www.qualtrics.com/support/integrations/api-integration/overview/)

2. Create `credentials.yaml.DEFAULT` in the `credentialDir` and add API token information

```
credentialDir='/Users/danicosme/' #replace with your path

if [ ! -f ${credentialDir}credentials.yaml.DEFAULT ]; then
  cd ${credentialDir}
  touch credentials.yaml.DEFAULT
  echo "user: dcosme#oregon" >> credentials.yaml.DEFAULT #replace with your token information
  echo "token: Ik0XNNQVZFdriLEnot..." >> credentials.yaml.DEFAULT #replace with your token information
else
  echo "credential file already exists in this location"
fi
```

```{r survey list}
# load credential file
credentials = scorequaltrics::creds_from_file(cred_file_location)

# filter
surveysAvail = scorequaltrics::get_surveys(credentials)
surveysFiltered = filter(surveysAvail, grepl(survey_name_filter, SurveyName))
```

## Get survey data
```{r get data}
surveys = scorequaltrics::get_survey_data(surveysFiltered,
                                          credentials, 
                                          pid_col = sid_column_name)
```

## Tidy data
```{r tidy}
surveys1 = surveys %>%
  mutate(Login = gsub("Dev", "DEV", Login),
         Login = gsub("dev", "DEV", Login),
         Login = ifelse(grepl("^[0-9]{3}$", Login), paste0("DEV", Login), Login),
         Login = ifelse(Login == "DEVO55", "DEV055", Login))
```

## Summarize
### Completed surveys
```{r summarize_complete}
surveys1 %>%
  filter(item == "Finished" & value == "1") %>%
  filter(!grepl(exclude_sid, Login) & !is.na(Login)) %>%
  #filter(grepl("DEV", Login)) %>%
  group_by(survey_name, Login) %>%
  summarize(n = n()) %>%
  spread(survey_name, n)
```

#### Dates for subs with >1 completed surveys
```{r}
(repeat.subs = surveys1 %>%
  filter(item == "Finished" & value == "1") %>%
  filter(!grepl(exclude_sid, Login) & !is.na(Login)) %>%
  group_by(survey_name, Login) %>%
  summarize(n = n()) %>%
  filter(n > 1) %>%
  spread(survey_name, n))

surveys1 %>%
  filter(item == "StartDate") %>%
  filter(Login %in% repeat.subs$Login) %>%
  group_by(survey_name, Login) %>%
  mutate(n = n()) %>%
  filter(n > 1)
```


### Incomplete surveys
```{r summarize_incomplete}
surveys1 %>%
  filter(item == "Finished" & value == "0") %>%
  filter(!grepl(exclude_sid, Login) & !is.na(Login)) %>%
  group_by(survey_name, Login) %>%
  summarize(n = n()) %>%
  spread(survey_name, n)
```

#### Dates for subs with >1 completed surveys
```{r}
(repeat.subs.inc = surveys1 %>%
  filter(item == "Finished" & value == "0") %>%
  filter(!grepl(exclude_sid, Login) & !is.na(Login)) %>%
  group_by(survey_name, Login) %>%
  summarize(n = n()) %>%
  filter(n > 1) %>%
  spread(survey_name, n))

surveys1 %>%
  filter(item == "StartDate") %>%
  filter(Login %in% repeat.subs.inc$Login) %>%
  group_by(survey_name, Login) %>%
  mutate(n = n()) %>%
  filter(n > 1)
```