---
title: "ROC descriptives"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# load packages
```{r}
library(tidyverse)
```

# define palettes
```{r}
instruction = c("#F21A00", "#3B9AB2")
```

# load tidied data
```{r}
source("load_data.R")
```

# check responses
Check if wrong buttons were used (i.e., not 5-8)

* DEV001 = code normally
* DEV011 = code normally
* DEV016 = code normally
* DEV017 = exclude; can't tell if they're missed responses or incorrect placement of fingers
* DEV019 = exclude; can't tell if they're missed responses or incorrect placement of fingers
* DEV020 = code normally
* DEV022 = code normally
* DEV028 = code normally
* DEV032 = incorrect placement of fingers; recode runs 1-2 (LOOK INTO WTP)
* DEV037 = exclude; technical error?
* DEV054 = exclude; technical error?
* DEV060 = code normally; task ended early
* DEV061 = code normally; task ended early
* DEV063 = code normally; task ended early
* DEV069 = incorrect placement of fingers in run1
* DEV075 = code normally
* DEV082 = code normally
* DEV083 = code normally

```{r}
subs = data.all %>%
  group_by(subjectID, run, rating) %>%
  summarize(n = n()) %>%
  spread(rating, n) %>%
  mutate(messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", NA)) %>%
  filter(messed == "yes") %>% 
  ungroup() %>% 
  select(subjectID) %>% 
  unique()

data.all %>%
  group_by(subjectID, run, rating) %>%
  summarize(n = n()) %>%
  spread(rating, n) %>%
  mutate(messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", NA)) %>%
  filter(subjectID %in% subs$subjectID)
```

# recode and exclude
Exclusions

* MRI motion and data quality exclusions: DEV001, DEV020, DEV032, DEV047, DEV055, DEV064, DEV066
* Button box exclusions: DEV017, DEV019, DEV037, DEV054

"DEV017", "DEV019", "DEV037", "DEV054"
"DEV032", "DEV069" run1

Recoding

* DEV069: recode runs1
```{r}
data.ex = data.all %>%
  filter(!subjectID %in% c("DEV001","DEV020","DEV032","DEV047","DEV055","DEV064","DEV066", "DEV017", "DEV019", "DEV037", "DEV054")) %>%
  mutate(rating = ifelse(subjectID == "DEV069" & run == "run1", rating - 1, rating),
         rating = ifelse(subjectID == "DEV069" & run == "run1" & is.na(rating), 8, rating),
         rating = rating - 4)
```

# repeated measures correlation between liking and bid value
```{r}
data.ex %>%
  ggplot(aes(liking_rating, rating, color = instruction)) +
    geom_point(position = "jitter", alpha = .3) + 
    geom_smooth(method = "lm") +
    scale_color_manual(values = instruction) +
    theme_minimal()

# average correlation overlaid on individual correlations
data.ex %>%
  ggplot(aes(liking_rating, rating, color = instruction)) +
    geom_line(aes(group = interaction(subjectID, instruction)), stat = "smooth", method = "lm", alpha = .2, se = FALSE) +
    geom_line(stat = "smooth", method = "lm", size = 1.5) +
    scale_color_manual(values = instruction) +
    theme_minimal()

# look
data.ex %>%
  filter(instruction == "look") %>%
  ungroup() %>%
  mutate(subjectID = as.factor(subjectID)) %>% 
  select(subjectID, liking_rating, rating) %>%
  rmcorr::rmcorr(subjectID, liking_rating, rating, .)

# regulate
data.ex %>%
  filter(instruction == "regulate") %>%
  ungroup() %>%
  mutate(subjectID = as.factor(subjectID)) %>% 
  select(subjectID, liking_rating, rating) %>%
  rmcorr::rmcorr(subjectID, liking_rating, rating, .)
```

# plot means as a function of instruction and craving condition
```{r}
data.ex %>%
  filter(!craving == "neutral") %>%
  mutate(craving = factor(craving, levels = c("not craved", "craved"))) %>%
  gather(type, rating, rating, liking_rating) %>%
  ggplot(aes(type, rating, fill = instruction, alpha = craving)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = instruction) +
    scale_y_continuous(limits = c(0,4)) +
    theme_minimal()

data.ex %>%
  ggplot(aes(rating, fill = instruction)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    scale_fill_manual(values = instruction) +
    theme_minimal()

data.ex %>%
  ggplot(aes(rating, fill = instruction)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    facet_grid(~craving) +
    scale_fill_manual(values = instruction) +
    theme_minimal()
```

# plot distribution of difference scores
* liking_rating = independent liking ratings from separate session
* rating = craving rating during the task
* positive diff = higher in the task, negative = higher pre-task
```{r}
data.ex %>%
  filter(!craving == "neutral") %>%
  mutate(diff = rating - liking_rating) %>%
  ggplot(aes(diff, fill = instruction)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    scale_fill_manual(values = instruction) +
    labs(x = "difference (task rating - pre-task rating)") +
    theme_minimal()

data.ex %>%
  filter(!craving == "neutral") %>%
  mutate(diff = rating - liking_rating,
         craving = factor(craving, levels = c("not craved", "craved"))) %>%
  ggplot(aes(diff, fill = instruction, alpha = craving)) +
    geom_histogram(position = "dodge", binwidth = .25) +
    scale_alpha_discrete(range = c(.6, 1)) +
    scale_fill_manual(values = instruction) +
    labs(x = "difference (task rating - pre-task rating)") +
    theme_minimal()
```

